Energy and the CES production function

### 2015-10-15 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Commented texreg code that uses extract.

<<stat_details_table, results="asis", include=FALSE, eval=FALSE>>=
texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
       dcolumn = TRUE, 
       booktabs = TRUE, 
       use.packages = FALSE, 
       label=paste0("tab:", opts_current$get("label")), 
       caption = "Example output from \\texttt{texreg}.",
       caption.above = TRUE, 
       digits = 6,
       fontsize = "tiny",
       float.pos = "hb")
@

>>>>

%' <<stat_details_table, results="asis", include=FALSE, eval=FALSE>>=
%' texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
%'        dcolumn = TRUE, 
%'        booktabs = TRUE, 
%'        use.packages = FALSE, 
%'        label=paste0("tab:", opts_current$get("label")), 
%'        caption = "Example output from \\texttt{texreg}.",
%'        caption.above = TRUE, 
%'        digits = 6,
%'        fontsize = "tiny",
%'        float.pos = "hb")
%' @
